---
title: "Past Benchmarking - Lao PDR"
author: "OECD Development Centre - MDCR Unit"
output: html_document
---

This page is a collection of the results for the Multi-dimensional Country Review's Past Benchmarking algorithm for the country **Lao PDR**. <br>

This algorithm finds an indicator's present day value for Lao PDR and searches for countries with similar levels in the past. Countries who have been at or near the same value become Benchmark Candidate Countries, which are then filtered further by a "goal" each of these countries have met. This goal is explicitly defined for each indicator and is adjusted by the application of the algorithm. The Candidate Countries are then summarized into a data table with information such as matching year, length of time to reach goal and other relevant information. A series of time series graphs for each of the Candidate Countries is also included to evaluate sustained performance over time. <br>

The uses of this algorithm are multi-faceted. Seeing how other, comparable countries have developed over time for an indicator can help us find stories in the past, provide reference points for effective policies and guide feasible goal-setting. 
<br>

The following indicators are currently available: <p>
* [Constant GDP per capita (2010 USD)](#GDP) <br>
* [Employment to population (%)](#Emp) <br>
* [Literacy rate (%)](#Lit)<br>
* [Mean years of schooling](#Mskool) <br>
* [Percent of population without schooling](#Noskool) <br>
* [Economic complexity index](#ECI) <br>
* [Output per worker (GDP constant 2010 USD)](#Lab) <br>
* [Historical GDP](#hist)<br>

The summary of the results for Lao PDR for each of these indicators are found below. 

---

#### **Indicator:** Constant GDP per capita (2010 USD) {#GDP} 

**Constant GDP per capita in Lao PDR in 2019 :** 1 840.50 USD <br>
**Match threshold :** ±250 USD<br> 
**Goal :** Double (2x) <br>
**Source :** WDI <p>

##### **Map of comparison countries**

Below is a map populated with each country that met the matching criteria. 

```{r , message=FALSE, fig.align = "center", class.source="bg-success", echo=FALSE}

library(maps)
library(rbokeh)
library(readxl)
library(dplyr)

setwd("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/")

caps<-read_excel("0_Indicator_Tables/map_figures.xlsx") 
caps <- caps[,-5]
gdp <- read_excel("0_Indicator_Tables/2019_LAO_gdp.xlsx")
names(gdp)[2]<-"country"

clist <- gdp$country
gdp$`Match value`<-round(gdp$`Match value`, digits=2)

caps<-subset(caps, country %in% clist)
info.cols<-gdp[,c(2:5,7)]
caps<-left_join(info.cols,caps)

indicators <- read_excel("Similarity measures/sim.indicators.xlsx")
indicators[,4:10] <- zoo::na.fill(indicators[,4:10], "extend")

ind.filter <- gdp[,2:3]
num <- nrow(gdp)
real.val <-""

for(i in 1:num){
  slice <- ind.filter[i,]
  list <- indicators[indicators$country==slice$country & indicators$year==slice$`Match year`, ]
  real.val <- rbind(real.val,list)
}

info.val <- real.val[-1,-c(1,11)]
info.val[3:9] <- sapply(info.val[3:9], as.numeric)
info.val[3:9]<-round(info.val[3:9], digits=2)
info.val$Land.area<-formatC(info.val$Land.area, format="d", big.mark=",")
info.val$Pop.density<-formatC(info.val$Pop.density, format="d", big.mark=",")
info.val$Population<-formatC(info.val$Population, format="d", big.mark=",")

caps<-merge(info.val,caps,by="country")

colnames(caps)[1]<-"Country"

figure(width = 800, height = 450, padding_factor = 0) %>%
  ly_map("world", col = "gray", line_color="black",line_alpha=0.5,fill_alpha=0.75) %>%
  ly_points(long, lat, data = caps, size = 10,
            hover = c(Country,`Match year`,
                      `Years to reach goal`,
                      Population,Land.area,
                      Pop.density,Industry,Services,Oil.rents,
                      Agriculture.land))
```

##### **Table output of comparison countries**

This table is a summary of the results of the algorithm.

```{r , message=FALSE, class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%"} 

library(readxl)
library(ggplot2)
library(foreach)
library(dplyr)
library(DT)
library(ggpubr)

# Upload excel of output of GDP function through changing file path ISO3C
gdp.output <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/0_Indicator_Tables/2019_LAO_gdp.xlsx")
# Upload similarity measure
sim.val <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/Similarity measures/LAO_similarity_list.xlsx", sheet = "gdp.sim.sum")
# Upload wb classifications
wb <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/wb_classification.xlsx")
gdp.output <- merge(wb,gdp.output)

# Keep only values wanted on table
sim.val <- sim.val[,c(1,9)]
colnames(sim.val)[1:2]<- c("Comparison country","Similarity value")
gdp.output <- merge(gdp.output,sim.val)

# Data cleaning
gdp.output <- gdp.output[,-3]
gdp.output <- gdp.output[,c(2,1,3:8)]
gdp.output$`Match value`<-round(gdp.output$`Match value`, digits=2)
gdp.output$`Value at goal`<-round(gdp.output$`Value at goal`, digits=2)
gdp.output$`Similarity value`<-round(gdp.output$`Similarity value`, digits=2)

# Data table of output
DT::datatable(gdp.output, rownames = FALSE)

```

##### **Time series of comparison countries**

These graphs show the full time series for the indicator. The solid line represents the comparison country whereas the dotted line is the time series for the country of interest, Lao PDR. The red dots indicate the match values for both countries. Finally, the vertical dashed lines show the window from which the country indicator value matched current day Lao PDR until it surpasses its goal.  

```{r , message=FALSE, class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%"} 
setwd("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/")

# Upload indicator database & output table
ind.db<-read_excel("indicator.db.xlsx")
gdp.output <- read_excel("0_Indicator_Tables/2019_LAO_gdp.xlsx")

# Parse out time series
indicator <- ind.db[,c(1:2,3)]
names(indicator)[3]<-"value"
indicator<-na.omit(indicator)
cname <-gdp.output$`Comparison country`
gdp.ts <- indicator[indicator$country %in% c("Lao PDR",cname) ,]
gdp.ts$country[gdp.ts$country=="Lao PDR"] <-"aaaLao PDR"

gdp.output <- gdp.output[order(gdp.output$`Comparison country`),]
gdp.ts <- gdp.ts[order(gdp.ts$country),]

# Set lists to create time series graphs
cname <-gdp.output$`Comparison country`
myear <- gdp.output$`Match year`
gyear <- gdp.output$`Year reached goal`
mval <- gdp.output$`Match value`

# Split ts by country
glist<-gdp.ts%>%
  group_split(country)

# Change COI # to the one of country of interest in glist then remove using same #
COI <- glist[[1]]
coi.current <- COI %>% filter(abs(year) == max(abs(year)))
cur.val <- coi.current$value
cur.year <- coi.current$year
glist<-glist[-1]

# Plotting function for every country 
# **** IMPORTANT: Change here xlim to match length of time window 
ts.plotter<-function(x){
  vertical.lines <- c(myear[x],gyear[x])

  ggplot(data = glist[[x]])  + theme_linedraw()+
    geom_line(aes(y = value, x = year))+
    geom_line(data = COI, aes(y=value, x=year), linetype=3,color="black")+
    labs(title=cname[[x]], x="Year",y="Constant GDP per capita")+
    theme(plot.title = element_text(hjust = 0.5))+
    geom_point(aes(x=myear[x],y=mval[x]), color="red")+
    geom_point(aes(x=cur.year,y=cur.val), color="red")+
    xlim(1960,2020)+
    geom_vline(xintercept=vertical.lines,
               linetype=2, colour="black")+
    annotate("rect", xmin=myear[x], xmax =gyear[x], ymin=-Inf, ymax=Inf,alpha = .1)+
    theme(axis.text = element_text(face="bold"))
}

num<-nrow(gdp.output)

# Plots graph for each country 
gdp.plots<-foreach(x=1:num) %do%
  ts.plotter(x)

# Graph upload
# ** IMPORTANT: Here # of plots will change by # of comparison countries (obs in envi)

for(i in 1:num)
{plot(gdp.plots[[i]])}

```

##### **Similarity measure**

In order to narrow down the list of candidate countries further, a similarity measure is constructed. To calculate this, we compare country structures through standardizing the values of certain structural indicators of the comparison country at the match year with present day Lao PDR. We calculate this value for seven indicators: <br>

*	Total land area (sq. km)<br>
*	Population density (people per sq. km of land area)<br>
*	Services, valued added (% of GDP)<br>
*	Industry (including construction), valued added (% of GDP)<br>
*	Oil rents (% of GDP)<br>
*	Agricultural land (% of land area)<br>
*	Total population<br>

The values closest to zero being the most similar to Lao PDR, when we sum these we want the smallest value possible. The results of this summation are seen above under Similarity Measure in the table of the algorithm's results. 

It also possible to compare using radar charts, which gives a global idea of which countries had similar values for each structural indicators. This makes it possible to compare countries when a particular structural indicator is more important for your comparison, such as by size, economic composition, etc.

```{r,fig.show="hold", out.width="33%",message=FALSE,echo=FALSE}
library(fmsb)
library(readxl)

sim.val <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/Similarity measures/LAO_similarity_list.xlsx", sheet = "gdp.sim.sum")
sim.val <- na.omit(sim.val)

setwd("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/")
gdp.output <- read_excel("0_Indicator_Tables/2019_LAO_gdp.xlsx")
gdp.output <- gdp.output[,c(2,3)]

colnames(gdp.output)[1]<-"country"
sim.val<-merge(sim.val,gdp.output,by="country")

sim.val <- arrange(sim.val, sum.std.val)
mytitle<-sim.val$country
myear <-sim.val$`Match year`

mytitle<-paste(mytitle,myear)
row <- nrow(sim.val)

wheel.slice <- sim.val[,-c(1,9:10)]

par(mar=rep(1,4))

for(i in 1:row){
  slice.1 <- wheel.slice[i,]
  slice.1 <- abs(slice.1)
  col <- ncol(slice.1)
  
  for(x in 1:col){
    slice.1[x]<-ifelse(slice.1[x] > 4, (slice.1[x]=4), slice.1[x])
  }
  
  max.1 <- max(slice.1)
  min.1 <- min(slice.1)
  data <- rbind(rep(0,1) , rep(max.1,1) , slice.1)
  data2 = data
  data2[2:1,] = data2[1:2,]
  data2[2:1,] = data2[1:2,]
  
  radarchart(data2, axistype = 2, 
             pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=2 ,
             cglcol="grey", cglty=1, axislabcol="grey",
             caxislabels=seq(1,1,-1), cglwd=0.9,
             vlcex=0.8,
             title=mytitle[i]
  )
}

```

[Back to top](#)

________

#### **Indicator:** Employment to population (%){#Emp}

**2019 Employment in Lao PDR :** 77.98% <br>
**Match threshold :** ±2.5% <br>
**Goal :** 1.25x
**Source**: WDI

```{r , message=FALSE, fig.align = "center", class.source="bg-success", echo=FALSE}

setwd("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/")

caps<-read_excel("0_Indicator_Tables/map_figures.xlsx") 
caps <- caps[,-5]
employ <- read_excel("0_Indicator_Tables/2019_LAO_employ.xlsx")
names(employ)[2]<-"country"

clist <- employ$country
employ$`Match value`<-round(employ$`Match value`, digits=2)

caps<-subset(caps, country %in% clist)
info.cols<-employ[,c(2:5,7)]
caps<-left_join(info.cols,caps)

indicators <- read_excel("Similarity measures/sim.indicators.xlsx")
indicators[,4:10] <- zoo::na.fill(indicators[,4:10], "extend")

ind.filter <- employ[,2:3]
num <- nrow(employ)
real.val <-""

for(i in 1:num){
  slice <- ind.filter[i,]
  list <- indicators[indicators$country==slice$country & indicators$year==slice$`Match year`, ]
  real.val <- rbind(real.val,list)
}

info.val <- real.val[-1,-c(1,11)]
info.val[3:9] <- sapply(info.val[3:9], as.numeric)
info.val[3:9]<-round(info.val[3:9], digits=2)
info.val$Land.area<-formatC(info.val$Land.area, format="d", big.mark=",")
info.val$Pop.density<-formatC(info.val$Pop.density, format="d", big.mark=",")
info.val$Population<-formatC(info.val$Population, format="d", big.mark=",")

caps<-merge(info.val,caps,by="country")

colnames(caps)[1]<-"Country"

figure(width = 800, height = 450, padding_factor = 0) %>%
  ly_map("world", col = "gray", line_color="black",line_alpha=0.5,fill_alpha=0.75) %>%
  ly_points(long, lat, data = caps, size = 10,
            hover = c(Country,`Match year`,
                      `Years to reach goal`,
                      Population,Land.area,
                      Pop.density,Industry,Services,Oil.rents,
                      Agriculture.land))
```

##### **Table output of comparison countries** 

```{r , message=FALSE, warning = FALSE, class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%"}
emp.output <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/0_Indicator_Tables/2019_LAO_employ.xlsx")
sim.val <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/Similarity measures/LAO_similarity_list.xlsx", sheet = "emp.sim.sum")
# Upload wb classifications
wb <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/wb_classification.xlsx")
emp.output <- merge(wb,emp.output)

sim.val <- sim.val[,c(1,9)]
colnames(sim.val)[1:2]<- c("Comparison country","Similarity value")
emp.output <- merge(emp.output,sim.val)

emp.output <- emp.output[,-3]
emp.output <- emp.output[,c(2,1,3:8)]
emp.output$`Match value`<-round(emp.output$`Match value`, digits=2)
emp.output$`Value at goal`<-round(emp.output$`Value at goal`, digits=2)
emp.output$`Similarity value`<-round(emp.output$`Similarity value`, digits=2)

DT::datatable(emp.output, rownames = FALSE)
```

##### **Time series of comparison countries** 

These graphs show the full time series for the indicator. The solid line represents the comparison country whereas the dotted line is the time series for the country of interest, Lao PDR. The red dots indicate the match values for both countries. Finally, the vertical dashed lines show the window from which the country indicator value matched current day Lao PDR until it surpasses its goal.  

```{r , message=FALSE, warning = FALSE, class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%"}
ind.db<-read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/indicator.db.xlsx")

indicator <- ind.db[,c(1:2,4)]
names(indicator)[3]<-"value"
indicator<-na.omit(indicator)
cname <-emp.output$`Comparison country`
emp.ts <- indicator[indicator$country %in% c("Lao PDR",cname) ,]
emp.ts$country[emp.ts$country=="Lao PDR"] <-"aaaLao PDR"

emp.output <- emp.output[order(emp.output$`Comparison country`),]
emp.ts <- emp.ts[order(gdp.ts$country),]

cname <-emp.output$`Comparison country`
myear <- emp.output$`Match year`
gyear <- emp.output$`Year reached goal`
mval <- emp.output$`Match value`

glist<-emp.ts%>%
  group_split(country)

COI <- glist[[1]]
coi.current <- COI %>% filter(abs(year) == max(abs(year)))
cur.val <- coi.current$value
cur.year <- coi.current$year
glist<-glist[-1]

ts.plotter<-function(x){
  vertical.lines <- c(myear[x],gyear[x])

  ggplot(data = glist[[x]])  + theme_linedraw()+
    geom_line(aes(y = value, x = year))+
    geom_line(data = COI, aes(y=value, x=year), linetype=3,color="black")+
    labs(title=cname[[x]], x="Year",y="Employment to population (%)")+
    theme(plot.title = element_text(hjust = 0.5))+
    geom_point(aes(x=myear[x],y=mval[x]), color="red")+
    geom_point(aes(x=cur.year,y=cur.val), color="red")+
    xlim(1991,2020)+
    geom_vline(xintercept=vertical.lines,
               linetype=2, colour="black")+
    annotate("rect", xmin=myear[x], xmax =gyear[x], ymin=-Inf, ymax=Inf,alpha = .1)+
    theme(axis.text = element_text(face="bold"))
}

num<-nrow(emp.output)

gdp.plots<-foreach(x=1:num) %do%
  ts.plotter(x)

for(i in 1:num)
  {plot(gdp.plots[[i]])}


```

##### **Similarity measure**

```{r,fig.show="hold", out.width="33%",message=FALSE,echo=FALSE}
library(fmsb)
library(readxl)

sim.val <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/Similarity measures/LAO_similarity_list.xlsx", sheet = "emp.sim.sum")

setwd("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/")
emp.output <- read_excel("0_Indicator_Tables/2019_LAO_employ.xlsx")
emp.output <- emp.output[,c(2,3)]

colnames(emp.output)[1]<-"country"
sim.val<-merge(sim.val,emp.output,by="country")

sim.val <- arrange(sim.val, sum.std.val)
mytitle<-sim.val$country
myear <-sim.val$`Match year`

mytitle<-paste(mytitle,myear)
row <- nrow(sim.val)

wheel.slice <- sim.val[,-c(1,9:10)]

par(mar=rep(1,4))

for(i in 1:row){
  slice.1 <- wheel.slice[i,]
  slice.1 <- abs(slice.1)
  col <- ncol(slice.1)
  
  for(x in 1:col){
    slice.1[x]<-ifelse(slice.1[x] > 4, (slice.1[x]=4), slice.1[x])
  }
  
  max.1 <- max(slice.1)
  min.1 <- min(slice.1)
  data <- rbind(rep(0,1) , rep(max.1,1) , slice.1)
  data2 = data
  data2[2:1,] = data2[1:2,]
  data2[2:1,] = data2[1:2,]
  
  radarchart(data2, axistype = 2, 
             pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=2 ,
             cglcol="grey", cglty=1, axislabcol="grey",
             caxislabels=seq(1,1,-1), cglwd=0.9,
             vlcex=0.8,
             title=mytitle[i]
  )
}
```

[Back to top](#)

________

#### **Indicator:** Mean years of schooling {#Mskool}

**2010 mean years of schooling in Lao PDR:** 4.57 years <br>
**Match threshold:** ±0.25 years <br>
**Goal:** 1.25x <br>
**Source:** Barro-Lee Education Attainment dataset<p>

```{r , message=FALSE, fig.align = "center", class.source="bg-success", echo=FALSE}

setwd("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/")

caps<-read_excel("0_Indicator_Tables/map_figures.xlsx") 
caps <- caps[,-5]
meanyrs <- read_excel("0_Indicator_Tables/2019_LAO_meanyrs.xlsx")
names(meanyrs)[2]<-"country"

clist <- meanyrs$country
meanyrs$`Match value`<-round(meanyrs$`Match value`, digits=2)

caps<-subset(caps, country %in% clist)
info.cols<-meanyrs[,c(2:5,7)]
caps<-left_join(info.cols,caps)

indicators <- read_excel("Similarity measures/sim.indicators.xlsx")
indicators[,4:10] <- zoo::na.fill(indicators[,4:10], "extend")

ind.filter <- meanyrs[,2:3]
num <- nrow(meanyrs)
real.val <-""

for(i in 1:num){
  slice <- ind.filter[i,]
  list <- indicators[indicators$country==slice$country & indicators$year==slice$`Match year`, ]
  real.val <- rbind(real.val,list)
}

info.val <- real.val[-1,-c(1,11)]
info.val[3:9] <- sapply(info.val[3:9], as.numeric)
info.val[3:9]<-round(info.val[3:9], digits=2)
info.val$Land.area<-formatC(info.val$Land.area, format="d", big.mark=",")
info.val$Pop.density<-formatC(info.val$Pop.density, format="d", big.mark=",")
info.val$Population<-formatC(info.val$Population, format="d", big.mark=",")

caps<-merge(info.val,caps,by="country")

colnames(caps)[1]<-"Country"

figure(width = 800, height = 450, padding_factor = 0) %>%
  ly_map("world", col = "gray", line_color="black",line_alpha=0.5,fill_alpha=0.75) %>%
  ly_points(long, lat, data = caps, size = 10,
            hover = c(Country,`Match year`,
                      `Years to reach goal`,
                      Population,Land.area,
                      Pop.density,Industry,Services,Oil.rents,
                      Agriculture.land))
```

##### **Table output of comparison countries**

```{r , class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%", message=FALSE}
myrs.output<- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/0_Indicator_Tables/2019_LAO_meanyrs.xlsx")
sim.val <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/Similarity measures/LAO_similarity_list.xlsx", sheet = "myears.sim.sum")
# Upload wb classifications
wb <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/wb_classification.xlsx")
myrs.output <- merge(wb,myrs.output)

sim.val <- sim.val[,c(1,9)]
colnames(sim.val)[1:2]<- c("Comparison country","Similarity value")
myrs.output <- merge(myrs.output,sim.val)

myrs.output <- myrs.output[,-3]
myrs.output <- myrs.output[,c(2,1,3:8)]
myrs.output$`Match value`<-round(myrs.output$`Match value`, digits=2)
myrs.output$`Value at goal`<-round(myrs.output$`Value at goal`, digits=2)
myrs.output$`Similarity value`<-round(myrs.output$`Similarity value`, digits=2)

DT::datatable(myrs.output, rownames = FALSE)
```

##### **Time series of comparison countries**

These graphs show the full time series for the indicator. The solid line represents the comparison country whereas the dotted line is the time series for the country of interest, Lao PDR. The red dots indicate the match values for both countries. Finally, the vertical dashed lines show the window from which the country indicator value matched current day Lao PDR until it surpasses its goal.  

```{r , class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%", message=FALSE}
ind.db<-read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/indicator.db.xlsx")

indicator <- ind.db[,c(1:2,7)]
names(indicator)[3]<-"value"
indicator<-na.omit(indicator)
cname <-myrs.output$`Comparison country`
myrs.ts <- indicator[indicator$country %in% c("Lao PDR",cname) ,]
myrs.ts$country[myrs.ts$country=="Lao PDR"] <-"aaaLao PDR"

myrs.ts <- myrs.ts[order(myrs.ts$country),]
myrs.output <- myrs.output[order(myrs.output$`Comparison country`),]

cname <-myrs.output$`Comparison country`
myear <- myrs.output$`Match year`
gyear <- myrs.output$`Year reached goal`
mval <- myrs.output$`Match value`

glist<-myrs.ts%>%
  group_split(country)

COI <- glist[[1]]
coi.current <- COI %>% filter(abs(year) == max(abs(year)))
cur.val <- coi.current$value
cur.year <- coi.current$year
glist<-glist[-1]

ts.plotter<-function(x){
  vertical.lines <- c(myear[x],gyear[x])

  ggplot(data = glist[[x]])  + theme_linedraw()+
    geom_line(aes(y = value, x = year))+
    geom_line(data = COI, aes(y=value, x=year), linetype=3,color="black")+
    labs(title=cname[[x]], x="Year",y="Mean years of schooling")+
    theme(plot.title = element_text(hjust = 0.5))+
    geom_point(aes(x=myear[x],y=mval[x]), color="red")+
    geom_point(aes(x=cur.year,y=cur.val), color="red")+
    xlim(1960,2010)+
    geom_vline(xintercept=vertical.lines,
               linetype=2, colour="black")+
    annotate("rect", xmin=myear[x], xmax =gyear[x], ymin=-Inf, ymax=Inf,alpha = .1)+
    theme(axis.text = element_text(face="bold"))
}

num<-nrow(myrs.output)

myrs.plots<-foreach(x=1:num) %do%
  ts.plotter(x)

for(i in 1:num)
  {plot(myrs.plots[[i]])}

```

##### **Similarity measure**

```{r,fig.show="hold", out.width="33%",message=FALSE,echo=FALSE}
library(fmsb)

sim.val <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/Similarity measures/LAO_similarity_list.xlsx", sheet = "myears.sim.sum")

setwd("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/")
myrs.output <- read_excel("0_Indicator_Tables/2019_LAO_meanyrs.xlsx")
myrs.output <- myrs.output[,c(2,3)]

colnames(myrs.output)[1]<-"country"
sim.val<-merge(sim.val,myrs.output,by="country")

sim.val <- arrange(sim.val, sum.std.val)
mytitle<-sim.val$country
myear <-sim.val$`Match year`

mytitle<-paste(mytitle,myear)
row <- nrow(sim.val)

wheel.slice <- sim.val[,-c(1,9:10)]

par(mar=rep(1,4))

for(i in 1:row){
  slice.1 <- wheel.slice[i,]
  slice.1 <- abs(slice.1)
  col <- ncol(slice.1)
  
  for(x in 1:col){
    slice.1[x]<-ifelse(slice.1[x] > 4, (slice.1[x]=4), slice.1[x])
  }
  
  max.1 <- max(slice.1)
  min.1 <- min(slice.1)
  data <- rbind(rep(0,1) , rep(max.1,1) , slice.1)
  data2 = data
  data2[2:1,] = data2[1:2,]
  data2[2:1,] = data2[1:2,]
  
  radarchart(data2, axistype = 2, 
             pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=2 ,
             cglcol="grey", cglty=1, axislabcol="grey",
             caxislabels=seq(1,1,-1), cglwd=0.9,
             vlcex=0.8,
             title=mytitle[i]
  )
}
```

[Back to top](#)

________

#### **Indicator:** Percent of population without schooling {#Noskool}

**2010 percentage of population with no schooling in Lao PDR :**  34.59% <br>
**Match threshold :** ±0.25% <br>
**Goal :** Half (-0.5x) <br>
**Source:** Barro-Lee Education Attainment dataset <p>

```{r , message=FALSE, fig.align = "center", class.source="bg-success", echo=FALSE}

setwd("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/")

caps<-read_excel("0_Indicator_Tables/map_figures.xlsx") 
caps <- caps[,-5]
noschool <- read_excel("0_Indicator_Tables/2019_LAO_noschool.xlsx")
names(noschool)[2]<-"country"

clist <- noschool$country
noschool$`Match value`<-round(noschool$`Match value`, digits=2)

caps<-subset(caps, country %in% clist)
info.cols<-noschool[,c(2:5,7)]
caps<-left_join(info.cols,caps)

indicators <- read_excel("Similarity measures/sim.indicators.xlsx")
indicators[,4:10] <- zoo::na.fill(indicators[,4:10], "extend")

ind.filter <- noschool[,2:3]
num <- nrow(noschool)
real.val <-""

for(i in 1:num){
  slice <- ind.filter[i,]
  list <- indicators[indicators$country==slice$country & indicators$year==slice$`Match year`, ]
  real.val <- rbind(real.val,list)
}

info.val <- real.val[-1,-c(1,11)]
info.val[3:9] <- sapply(info.val[3:9], as.numeric)
info.val[3:9]<-round(info.val[3:9], digits=2)
info.val$Land.area<-formatC(info.val$Land.area, format="d", big.mark=",")
info.val$Pop.density<-formatC(info.val$Pop.density, format="d", big.mark=",")
info.val$Population<-formatC(info.val$Population, format="d", big.mark=",")

caps<-merge(info.val,caps,by="country")

colnames(caps)[1]<-"Country"

figure(width = 800, height = 450, padding_factor = 0) %>%
  ly_map("world", col = "gray", line_color="black",line_alpha=0.5,fill_alpha=0.75) %>%
  ly_points(long, lat, data = caps, size = 10,
            hover = c(Country,`Match year`,
                      `Years to reach goal`,
                      Population,Land.area,
                      Pop.density,Industry,Services,Oil.rents,
                      Agriculture.land))
```

##### **Table output of comparison countries**

```{r , message=FALSE, class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%"}
noskl.output<-read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/0_Indicator_Tables/2019_LAO_noschool.xlsx")
sim.val <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/Similarity measures/LAO_similarity_list.xlsx", sheet = "noskl.sim.sum")
# Upload wb classifications
wb <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/wb_classification.xlsx")
noskl.output <- merge(wb,noskl.output)

sim.val <- sim.val[,c(1,9)]
colnames(sim.val)[1:2]<- c("Comparison country","Similarity value")
noskl.output <- merge(noskl.output,sim.val)

noskl.output <- noskl.output[,-3]
noskl.output <- noskl.output[,c(2,1,3:8)]
noskl.output$`Match value`<-round(noskl.output$`Match value`, digits=2)
noskl.output$`Value at goal`<-round(noskl.output$`Value at goal`, digits=2)
noskl.output$`Similarity value`<-round(noskl.output$`Similarity value`, digits=2)

DT::datatable(noskl.output, rownames = FALSE)
```

##### **Time series of comparison countries**

These graphs show the full time series for the indicator. The solid line represents the comparison country whereas the dotted line is the time series for the country of interest, Lao PDR. The red dots indicate the match values for both countries. Finally, the vertical dashed lines show the window from which the country indicator value matched current day Lao PDR until it surpasses its goal.  

```{r , message=FALSE, class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%"}
ind.db<-read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/indicator.db.xlsx")

indicator <- ind.db[,c(1:2,6)]
names(indicator)[3]<-"value"
indicator<-na.omit(indicator)
cname <-noskl.output$`Comparison country`
noskl.ts <- indicator[indicator$country %in% c("Lao PDR",cname) ,]
noskl.ts$country[noskl.ts$country=="Lao PDR"] <-"aaaLao PDR"

noskl.output <- noskl.output[order(noskl.output$`Comparison country`),]
noskl.ts <- noskl.ts[order(noskl.ts$country),]

cname <-noskl.output$`Comparison country`
myear <- noskl.output$`Match year`
gyear <- noskl.output$`Year reached goal`
mval <- noskl.output$`Match value`

glist<-noskl.ts%>%
  group_split(country)

COI <- glist[[1]]
coi.current <- COI %>% filter(abs(year) == max(abs(year)))
cur.val <- coi.current$value
cur.year <- coi.current$year
glist<-glist[-1]

ts.plotter<-function(x){
  vertical.lines <- c(myear[x],gyear[x])

  ggplot(data = glist[[x]])  + theme_linedraw()+
    geom_line(aes(y = value, x = year))+
    geom_line(data = COI, aes(y=value, x=year), linetype=3,color="black")+
    labs(title=cname[[x]], x="Year",y="Population without schooling (%)")+
    theme(plot.title = element_text(hjust = 0.5))+
    geom_point(aes(x=myear[x],y=mval[x]), color="red")+
    geom_point(aes(x=cur.year,y=cur.val), color="red")+
    xlim(1960,2010)+
    geom_vline(xintercept=vertical.lines,
               linetype=2, colour="black")+
    annotate("rect", xmin=myear[x], xmax =gyear[x], ymin=-Inf, ymax=Inf,alpha = .1)+
    theme(axis.text = element_text(face="bold"))
}

num<-nrow(noskl.output)

noskl.plots<-foreach(x=1:num) %do%
  ts.plotter(x)

for(i in 1:num)
  {plot(noskl.plots[[i]])}

```

##### **Similarity measure**

```{r,fig.show="hold", out.width="33%",message=FALSE,echo=FALSE}
library(fmsb)

sim.val <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/Similarity measures/LAO_similarity_list.xlsx", sheet = "noskl.sim.sum")

setwd("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/")
nskl.output <- read_excel("0_Indicator_Tables/2019_LAO_noschool.xlsx")
nskl.output <- nskl.output[,c(2,3)]

colnames(nskl.output)[1]<-"country"
sim.val<-merge(sim.val,nskl.output,by="country")

sim.val <- arrange(sim.val, sum.std.val)
mytitle<-sim.val$country
myear <-sim.val$`Match year`

mytitle<-paste(mytitle,myear)
row <- nrow(sim.val)

wheel.slice <- sim.val[,-c(1,9:10)]

par(mar=rep(1,4))

for(i in 1:row){
  slice.1 <- wheel.slice[i,]
  slice.1 <- abs(slice.1)
  col <- ncol(slice.1)
  
  for(x in 1:col){
    slice.1[x]<-ifelse(slice.1[x] > 4, (slice.1[x]=4), slice.1[x])
  }
  
  max.1 <- max(slice.1)
  min.1 <- min(slice.1)
  data <- rbind(rep(0,1) , rep(max.1,1) , slice.1)
  data2 = data
  data2[2:1,] = data2[1:2,]
  data2[2:1,] = data2[1:2,]
  
  radarchart(data2, axistype = 2, 
             pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=2 ,
             cglcol="grey", cglty=1, axislabcol="grey",
             caxislabels=seq(1,1,-1), cglwd=0.9,
             vlcex=0.8,
             title=mytitle[i]
  )
}
```

[Back to top](#)

________

#### **Indicator:** Economic complexity index {#ECI}

**2019 economic complexity in Lao PDR :** -1.251 <br>
**Match threshold :** ±0.01 <br>
**Goal :** +0.5 <br>
**Source:** OEC <p>

```{r , message=FALSE, fig.align = "center", class.source="bg-success", echo=FALSE}

setwd("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/")

caps<-read_excel("0_Indicator_Tables/map_figures.xlsx") 
caps <- caps[,-5]
eci <- read_excel("0_Indicator_Tables/2019_LAO_eci.xlsx")
names(eci)[2]<-"country"

clist <- eci$country
eci$`Match value`<-round(eci$`Match value`, digits=2)

caps<-subset(caps, country %in% clist)
info.cols<-eci[,c(2:5,7)]
caps<-left_join(info.cols,caps)

indicators <- read_excel("Similarity measures/sim.indicators.xlsx")
indicators[,4:10] <- zoo::na.fill(indicators[,4:10], "extend")

ind.filter <- eci[,2:3]
num <- nrow(eci)
real.val <-""

for(i in 1:num){
  slice <- ind.filter[i,]
  list <- indicators[indicators$country==slice$country & indicators$year==slice$`Match year`, ]
  real.val <- rbind(real.val,list)
}

info.val <- real.val[-1,-c(1,11)]
info.val[3:9] <- sapply(info.val[3:9], as.numeric)
info.val[3:9]<-round(info.val[3:9], digits=2)
info.val$Land.area<-formatC(info.val$Land.area, format="d", big.mark=",")
info.val$Pop.density<-formatC(info.val$Pop.density, format="d", big.mark=",")
info.val$Population<-formatC(info.val$Population, format="d", big.mark=",")

caps<-merge(info.val,caps,by="country")

colnames(caps)[1]<-"Country"

figure(width = 800, height = 450, padding_factor = 0) %>%
  ly_map("world", col = "gray", line_color="black",line_alpha=0.5,fill_alpha=0.75) %>%
  ly_points(long, lat, data = caps, size = 10,
            hover = c(Country,`Match year`,
                      `Years to reach goal`,
                      Population,Land.area,
                      Pop.density,Industry,Services,Oil.rents,
                      Agriculture.land))
```

##### **Table output of comparison countries**

```{r , class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%", message=FALSE}
eci.output<-read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/0_Indicator_Tables/2019_LAO_eci.xlsx")
sim.val <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/Similarity measures/LAO_similarity_list.xlsx", sheet = "eci.sim.sum")
# Upload wb classifications
wb <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/wb_classification.xlsx")
eci.output <- merge(wb,eci.output)

sim.val <- sim.val[,c(1,9)]
colnames(sim.val)[1:2]<- c("Comparison country","Similarity value")
eci.output <- merge(eci.output,sim.val)

eci.output <- eci.output[,-3]
eci.output <- eci.output[,c(2,1,3:8)]
eci.output$`Match value`<-round(eci.output$`Match value`, digits=2)
eci.output$`Value at goal`<-round(eci.output$`Value at goal`, digits=2)
eci.output$`Similarity value`<-round(eci.output$`Similarity value`, digits=2)

DT::datatable(eci.output, rownames = FALSE)
```

##### **Time series of comparison countries**

These graphs show the full time series for the indicator. The solid line represents the comparison country whereas the dotted line is the time series for the country of interest, Lao PDR. The red dots indicate the match values for both countries. Finally, the vertical dashed lines show the window from which the country indicator value matched current day Lao PDR until it surpasses its goal.  

```{r , class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%", message=FALSE}
ind.db<-read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/indicator.db.xlsx")

indicator <- ind.db[,c(1:2,8)]
names(indicator)[3]<-"value"
indicator<-na.omit(indicator)
cname <-eci.output$`Comparison country`
eci.ts <- indicator[indicator$country %in% c("Lao PDR",cname) ,]
eci.ts$country[eci.ts$country=="Lao PDR"] <-"aaaLao PDR"

eci.output <- eci.output[order(eci.output$`Comparison country`),]
eci.ts <- eci.ts[order(eci.ts$country),]

cname <-eci.output$`Comparison country`
myear <- eci.output$`Match year`
gyear <- eci.output$`Year reached goal`
mval <- eci.output$`Match value`

glist<-eci.ts%>%
  group_split(country)

COI <- glist[[1]]
coi.current <- COI %>% filter(abs(year) == max(abs(year)))
cur.val <- coi.current$value
cur.year <- coi.current$year
glist<-glist[-1]

ts.plotter<-function(x){
  vertical.lines <- c(myear[x],gyear[x])

  ggplot(data = glist[[x]])  + theme_linedraw()+
    geom_line(aes(y = value, x = year))+
    geom_line(data = COI, aes(y=value, x=year), linetype=3,color="black")+
    labs(title=cname[[x]], x="Year",y="Economic complexity index")+
    theme(plot.title = element_text(hjust = 0.5))+
    geom_point(aes(x=myear[x],y=mval[x]), color="red")+
    geom_point(aes(x=cur.year,y=cur.val), color="red")+
    xlim(1964,2020)+
    geom_vline(xintercept=vertical.lines,
               linetype=2, colour="black")+
    annotate("rect", xmin=myear[x], xmax =gyear[x], ymin=-Inf, ymax=Inf,alpha = .1)+
    theme(axis.text = element_text(face="bold"))
}

num<-nrow(eci.output)

eci.plots<-foreach(x=1:num) %do%
  ts.plotter(x)

for(i in 1:num)
  {plot(eci.plots[[i]])}

```

##### **Similarity measure**

```{r,fig.show="hold", out.width="33%",message=FALSE,echo=FALSE}
library(fmsb)

sim.val <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/Similarity measures/LAO_similarity_list.xlsx", sheet = "eci.sim.sum")

setwd("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/")
eci.output <- read_excel("0_Indicator_Tables/2019_LAO_eci.xlsx")
eci.output <- eci.output[,c(2,3)]

colnames(eci.output)[1]<-"country"
sim.val<-merge(sim.val,eci.output,by="country")

sim.val <- arrange(sim.val, sum.std.val)
mytitle<-sim.val$country
myear <-sim.val$`Match year`

mytitle<-paste(mytitle,myear)
row <- nrow(sim.val)

wheel.slice <- sim.val[,-c(1,9:10)]

par(mar=rep(1,4))

for(i in 1:row){
  slice.1 <- wheel.slice[i,]
  slice.1 <- abs(slice.1)
  col <- ncol(slice.1)
  
  for(x in 1:col){
    slice.1[x]<-ifelse(slice.1[x] > 4, (slice.1[x]=4), slice.1[x])
  }
  
  max.1 <- max(slice.1)
  min.1 <- min(slice.1)
  data <- rbind(rep(0,1) , rep(max.1,1) , slice.1)
  data2 = data
  data2[2:1,] = data2[1:2,]
  data2[2:1,] = data2[1:2,]
  
  radarchart(data2, axistype = 2, 
             pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=2 ,
             cglcol="grey", cglty=1, axislabcol="grey",
             caxislabels=seq(1,1,-1), cglwd=0.9,
             vlcex=0.8,
             title=mytitle[i]
  )
}
```

[Back to top](#)

________

#### **Indicator:** Output (GDP constant 2010 USD) per worker {#Lab}

**Output per worker in Lao PDR in 2019:** 3 552.04 USD <br>
**Match threshold :** ±250 USD <br>
**Goal :** 1.5x <br>
**Source:** ILO <p>

```{r , message=FALSE, fig.align = "center", class.source="bg-success", echo=FALSE}

setwd("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/")

caps<-read_excel("0_Indicator_Tables/map_figures.xlsx") 
caps <- caps[,-5]
lab <- read_excel("0_Indicator_Tables/2019_LAO_lab.xlsx")
names(lab)[2]<-"country"

clist <- lab$country
lab$`Match value`<-round(lab$`Match value`, digits=2)

caps<-subset(caps, country %in% clist)
info.cols<-lab[,c(2:5,7)]
caps<-left_join(info.cols,caps)

indicators <- read_excel("Similarity measures/sim.indicators.xlsx")
indicators[,4:10] <- zoo::na.fill(indicators[,4:10], "extend")

ind.filter <- lab[,2:3]
num <- nrow(lab)
real.val <-""

for(i in 1:num){
  slice <- ind.filter[i,]
  list <- indicators[indicators$country==slice$country & indicators$year==slice$`Match year`, ]
  real.val <- rbind(real.val,list)
}

info.val <- real.val[-1,-c(1,11)]
info.val[3:9] <- sapply(info.val[3:9], as.numeric)
info.val[3:9]<-round(info.val[3:9], digits=2)
info.val$Land.area<-formatC(info.val$Land.area, format="d", big.mark=",")
info.val$Pop.density<-formatC(info.val$Pop.density, format="d", big.mark=",")
info.val$Population<-formatC(info.val$Population, format="d", big.mark=",")

caps<-merge(info.val,caps,by="country")

colnames(caps)[1]<-"Country"

figure(width = 800, height = 450, padding_factor = 0) %>%
  ly_map("world", col = "gray", line_color="black",line_alpha=0.5,fill_alpha=0.75) %>%
  ly_points(long, lat, data = caps, size = 10,
            hover = c(Country,`Match year`,
                      `Years to reach goal`,
                      Population,Land.area,
                      Pop.density,Industry,Services,Oil.rents,
                      Agriculture.land))
```

##### **Table output of comparison countries**

```{r , message=FALSE, class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%"}
lab.output<-read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/0_Indicator_Tables/2019_LAO_lab.xlsx")
sim.val <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/Similarity measures/LAO_similarity_list.xlsx", sheet = "lab.sim.sum")
# Upload wb classifications
wb <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/wb_classification.xlsx")
lab.output <- merge(wb,lab.output)

sim.val <- sim.val[,c(1,9)]
colnames(sim.val)[1:2]<- c("Comparison country","Similarity value")
lab.output <- merge(lab.output,sim.val)

lab.output <- lab.output[,-3]
lab.output <- lab.output[,c(2,1,3:8)]
lab.output$`Match value`<-round(lab.output$`Match value`, digits=2)
lab.output$`Value at goal`<-round(lab.output$`Value at goal`, digits=2)
lab.output$`Similarity value`<-round(lab.output$`Similarity value`, digits=2)

DT::datatable(lab.output, rownames = FALSE)
```

##### **Time series of comparison countries**

These graphs show the full time series for the indicator. The solid line represents the comparison country whereas the dotted line is the time series for the country of interest, Lao PDR. The red dots indicate the match values for both countries. Finally, the vertical dashed lines show the window from which the country indicator value matched current day Lao PDR until it surpasses its goal.  

```{r , message=FALSE, class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%"}

ind.db<-read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/indicator.db.xlsx")

indicator <- ind.db[,c(1:2,9)]
names(indicator)[3]<-"value"
indicator<-na.omit(indicator)
cname <-lab.output$`Comparison country`
lab.ts <- indicator[indicator$country %in% c("Lao PDR",cname) ,]
lab.ts$country[lab.ts$country=="Lao PDR"] <-"aaaLao PDR"

lab.output <- lab.output[order(lab.output$`Comparison country`),]
lab.ts <- lab.ts[order(lab.ts$country),]

cname <-lab.output$`Comparison country`
myear <- lab.output$`Match year`
gyear <- lab.output$`Year reached goal`
mval <- lab.output$`Match value`

glist<-lab.ts%>%
  group_split(country)

COI <- glist[[1]]
coi.current <- COI %>% filter(abs(year) == max(abs(year)))
cur.val <- coi.current$value
cur.year <- coi.current$year
glist<-glist[-1]

ts.plotter<-function(x){
  vertical.lines <- c(myear[x],gyear[x])

  ggplot(data = glist[[x]])  + theme_linedraw()+
    geom_line(aes(y = value, x = year))+
    geom_line(data = COI, aes(y=value, x=year), linetype=3,color="black")+
    labs(title=cname[[x]], x="Year",y="Output per worker (GDP constant 2010 USD)")+
    theme(plot.title = element_text(hjust = 0.5),
          axis.text = element_text(face="bold",size=10))+
    geom_point(aes(x=myear[x],y=mval[x]), color="red")+
    geom_point(aes(x=cur.year,y=cur.val), color="red")+
    xlim(1991,2020)+
    geom_vline(xintercept=vertical.lines,
               linetype=2, colour="black")+
    annotate("rect", xmin=myear[x], xmax =gyear[x], ymin=-Inf, ymax=Inf,alpha = .1)
}

num<-nrow(lab.output)

lab.plots<-foreach(x=1:num) %do%
  ts.plotter(x)

for(i in 1:num)
  {plot(lab.plots[[i]])}

```

##### **Similarity measure**

```{r,fig.show="hold", out.width="33%",message=FALSE,echo=FALSE}
library(fmsb)

sim.val <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/Similarity measures/LAO_similarity_list.xlsx", sheet = "lab.sim.sum")

setwd("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/")
lab.output <- read_excel("0_Indicator_Tables/2019_LAO_lab.xlsx")
lab.output <- lab.output[,c(2,3)]

colnames(lab.output)[1]<-"country"
sim.val<-merge(sim.val,lab.output,by="country")

sim.val <- arrange(sim.val, sum.std.val)
mytitle<-sim.val$country
myear <-sim.val$`Match year`

mytitle<-paste(mytitle,myear)
row <- nrow(sim.val)

wheel.slice <- sim.val[,-c(1,9:10)]

par(mar=rep(1,4))

for(i in 1:row){
  slice.1 <- wheel.slice[i,]
  slice.1 <- abs(slice.1)
  col <- ncol(slice.1)
  
  for(x in 1:col){
    slice.1[x]<-ifelse(slice.1[x] > 4, (slice.1[x]=4), slice.1[x])
  }
  
  max.1 <- max(slice.1)
  min.1 <- min(slice.1)
  data <- rbind(rep(0,1) , rep(max.1,1) , slice.1)
  data2 = data
  data2[2:1,] = data2[1:2,]
  data2[2:1,] = data2[1:2,]
  
  radarchart(data2, axistype = 2, 
             pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=2 ,
             cglcol="grey", cglty=1, axislabcol="grey",
             caxislabels=seq(1,1,-1), cglwd=0.9,
             vlcex=0.8,
             title=mytitle[i]
  )
}
```

[Back to top](#)

________

#### **Indicator:** Literacy rate (%){#Lit}

**2018 literacy rate in Lao PDR :** 84.6%<br>
**Match threshold :** ±1.0% <br>
**Goal :** 1.25x <br>
**Source:** WDI <p>

```{r , message=FALSE, fig.align = "center", class.source="bg-success", echo=FALSE}
setwd("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/")

caps<-read_excel("0_Indicator_Tables/map_figures.xlsx") 
caps <- caps[,-5]
lit <- read_excel("0_Indicator_Tables/2019_LAO_liter.xlsx")
names(lit)[2]<-"country"

clist <- lit$country
lit$`Match value`<-round(lit$`Match value`, digits=2)

caps<-subset(caps, country %in% clist)
info.cols<-lit[,c(2:5,7)]
caps<-left_join(info.cols,caps)

indicators <- read_excel("Similarity measures/sim.indicators.xlsx")
indicators[,4:10] <- zoo::na.fill(indicators[,4:10], "extend")

ind.filter <- lit[,2:3]
num <- nrow(lit)
real.val <-""

for(i in 1:num){
  slice <- ind.filter[i,]
  list <- indicators[indicators$country==slice$country & indicators$year==slice$`Match year`, ]
  real.val <- rbind(real.val,list)
}

info.val <- real.val[-1,-c(1,11)]
info.val[3:9] <- sapply(info.val[3:9], as.numeric)
info.val[3:9]<-round(info.val[3:9], digits=2)
info.val$Land.area<-formatC(info.val$Land.area, format="d", big.mark=",")
info.val$Pop.density<-formatC(info.val$Pop.density, format="d", big.mark=",")
info.val$Population<-formatC(info.val$Population, format="d", big.mark=",")

caps<-merge(info.val,caps,by="country")

colnames(caps)[1]<-"Country"

figure(width = 800, height = 450, padding_factor = 0) %>%
  ly_map("world", col = "gray", line_color="black",line_alpha=0.5,fill_alpha=0.75) %>%
  ly_points(long, lat, data = caps, size = 10,
            hover = c(Country,`Match year`,
                      `Years to reach goal`,
                      Population,Land.area,
                      Pop.density,Industry,Services,Oil.rents,
                      Agriculture.land))
```

##### **Table output of comparison countries**

```{r , message=FALSE, class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%"}
library(readxl)

lit.output<-read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/0_Indicator_Tables/2019_LAO_liter.xlsx")
sim.val <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/Similarity measures/LAO_similarity_list.xlsx", sheet = "lit.sim.sum")
# Upload wb classifications
wb <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/wb_classification.xlsx")
lit.output <- merge(wb,lit.output)

sim.val <- sim.val[,c(1,9)]
colnames(sim.val)[1:2]<- c("Comparison country","Similarity value")
lit.output <- merge(lit.output,sim.val)

lit.output <- lit.output[,-3]
lit.output <- lit.output[,c(2,1,3:8)]
lit.output$`Match value`<-round(lit.output$`Match value`, digits=2)
lit.output$`Value at goal`<-round(lit.output$`Value at goal`, digits=2)
lit.output$`Similarity value`<-round(lit.output$`Similarity value`, digits=2)

DT::datatable(lit.output, rownames = FALSE)
```

##### **Time series of comparison countries**

These graphs show the full time series for the indicator. The solid line represents the comparison country whereas the dotted line is the time series for the country of interest, Lao PDR. The red dots indicate the match values for both countries. Finally, the vertical dashed lines show the window from which the country indicator value matched current day Lao PDR until it surpasses its goal.  

```{r , message=FALSE, class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%"}
ind.db<-read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/indicator.db.xlsx")

indicator <- ind.db[,c(1:2,5)]
names(indicator)[3]<-"value"
indicator<-na.omit(indicator)
cname <-lit.output$`Comparison country`
lit.ts <- indicator[indicator$country %in% c("Lao PDR",cname) ,]
lit.ts$country[lit.ts$country=="Lao PDR"] <-"aaaLao PDR"

lit.output <- lit.output[order(lit.output$`Comparison country`),]
lit.ts <- lit.ts[order(lit.ts$country),]

cname <-lit.output$`Comparison country`
myear <- lit.output$`Match year`
gyear <- lit.output$`Year reached goal`
mval <- lit.output$`Match value`

glist<-lit.ts%>%
  group_split(country)

COI <- glist[[1]]
coi.current <- COI %>% filter(abs(year) == max(abs(year)))
cur.val <- coi.current$value
cur.year <- coi.current$year
glist<-glist[-1]

ts.plotter<-function(x){
  vertical.lines <- c(myear[x],gyear[x])

  ggplot(data = glist[[x]])  + theme_linedraw()+
    geom_line(aes(y = value, x = year))+
    geom_line(data = COI, aes(y=value, x=year), linetype=3,color="black")+
    labs(title=cname[[x]], x="Year",y="Literacy rate (%)")+
    theme(plot.title = element_text(hjust = 0.5),
          axis.text = element_text(face="bold",size=10))+
    geom_point(aes(x=myear[x],y=mval[x]), color="red")+
    geom_point(aes(x=cur.year,y=cur.val), color="red")+
    xlim(1972,2020)+
    geom_vline(xintercept=vertical.lines,
               linetype=2, colour="black")+
    annotate("rect", xmin=myear[x], xmax =gyear[x], ymin=-Inf, ymax=Inf,alpha = .1)
}

num<-nrow(lit.output)

lit.plots<-foreach(x=1:num) %do%
  ts.plotter(x)

for(i in 1:num)
  {plot(lit.plots[[i]])}

```

##### **Similarity measure**

```{r,fig.show="hold", out.width="33%",message=FALSE,echo=FALSE}
library(fmsb)

sim.val <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/Similarity measures/LAO_similarity_list.xlsx", sheet = "lit.sim.sum")

setwd("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/")
lit.output <- read_excel("0_Indicator_Tables/2019_LAO_liter.xlsx")
lit.output <- lit.output[,c(2,3)]

colnames(lit.output)[1]<-"country"
sim.val<-merge(sim.val,lit.output,by="country")

sim.val <- arrange(sim.val, sum.std.val)
mytitle<-sim.val$country
myear <-sim.val$`Match year`

mytitle<-paste(mytitle,myear)
row <- nrow(sim.val)

wheel.slice <- sim.val[,-c(1,9:10)]

par(mar=rep(1,4))

for(i in 1:row){
  slice.1 <- wheel.slice[i,]
  slice.1 <- abs(slice.1)
  col <- ncol(slice.1)
  
  for(x in 1:col){
    slice.1[x]<-ifelse(slice.1[x] > 4, (slice.1[x]=4), slice.1[x])
  }
  
  max.1 <- max(slice.1)
  min.1 <- min(slice.1)
  data <- rbind(rep(0,1) , rep(max.1,1) , slice.1)
  data2 = data
  data2[2:1,] = data2[1:2,]
  data2[2:1,] = data2[1:2,]
  
  radarchart(data2, axistype = 2, 
             pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=2 ,
             cglcol="grey", cglty=1, axislabcol="grey",
             caxislabels=seq(1,1,-1), cglwd=0.9,
             vlcex=0.8,
             title=mytitle[i]
  )
}
```

[Back to top](#)

________

#### **Indicator:** Real GDP per capita in 2011 USD {#hist}

**Real GDP in Laos PDR in 2018:** 6 450.90 USD <br>
**Match threshold :** ±25 <br>
**Goal :** 2x (Doubled) <br>
**Source**: Maddison Project Database <br>

##### **Table output of comparison countries** 

```{r , message=FALSE, warning = FALSE, class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%"}
library(readxl)

hist.output <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/0_Indicator_Tables/LAO_historical.xlsx")
# Upload wb classifications
wb <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/wb_classification.xlsx")
hist.output <- merge(wb,hist.output)

hist.output <- hist.output[,-3]
hist.output <- hist.output[,c(2,1,3:7)]
hist.output$`Match value`<-round(hist.output$`Match value`, digits=2)
hist.output$`Value at goal`<-round(hist.output$`Value at goal`, digits=2)

DT::datatable(hist.output, rownames = FALSE)
```

##### **Time series of comparison countries** 

These graphs show the full time series for the indicator. The solid line represents the comparison country whereas the dotted line is the time series for the country of interest, El Salvador. The red dots indicate the match values for both countries. Finally, the vertical dashed lines show the window from which the country indicator value matched current day El Salvador until it surpasses its goal.  

```{r , message=FALSE, warning = FALSE, class.source="bg-success", echo=FALSE, fig.show="hold", out.width="50%"}
library(tidyverse)
library(foreach)

hist.output <- read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/0_Indicator_Tables/LAO_historical.xlsx")
ind.db<-read_excel("~/Desktop/OECD/DEV-Multi-dimensional Reviews - Past Benchmarking Tool/Past_Benchmarking/mpd2020.xlsx", sheet="Full data")

indicator <- ind.db[,c(2:4)]
names(indicator)[3]<-"value"
indicator<-na.omit(indicator)
cname <-hist.output$`Comparison country`
hist.ts <- indicator[indicator$country %in% c("Lao People's DR",cname) ,]
hist.ts$country[hist.ts$country=="Lao People's DR"] <-"aaaLao People's DR"

hist.output <- hist.output[order(hist.output$`Comparison country`),]
hist.ts <- hist.ts[order(hist.ts$country),]

cname <-hist.output$`Comparison country`
myear <- hist.output$`Match year`
gyear <- hist.output$`Year reached goal`
mval <- hist.output$`Match value`

glist<-hist.ts%>%
  group_split(country)

COI <- glist[[1]]
coi.current <- COI %>% filter(abs(year) == max(abs(year)))
cur.val <- coi.current$value
cur.year <- coi.current$year
glist<-glist[-1]

ts.plotter<-function(x){
  vertical.lines <- c(myear[x],gyear[x])

  ggplot(data = glist[[x]])  + theme_linedraw()+
    geom_line(aes(y = value, x = year))+
    geom_line(data = COI, aes(y=value, x=year), linetype=3,color="black")+
    labs(title=cname[[x]], x="Year",y="Real GDP (2011 USD)")+
    theme(plot.title = element_text(hjust = 0.5))+
    geom_point(aes(x=myear[x],y=mval[x]), color="red")+
    geom_point(aes(x=cur.year,y=cur.val), color="red")+
    xlim(1900,2020)+
    geom_vline(xintercept=vertical.lines,
               linetype=2, colour="black")+
    annotate("rect", xmin=myear[x], xmax =gyear[x], ymin=-Inf, ymax=Inf,alpha = .1)+
    theme(axis.text = element_text(face="bold"))
}

num<-nrow(hist.output)

gdp.plots<-foreach(x=1:num) %do%
  ts.plotter(x)

for(i in 1:num)
  {plot(gdp.plots[[i]])}


```

[Back to top](#)



